### 2022-02-16 ANA-TOPQ-2019-17-PAPER-metadata.tex

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------

% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current $tqH$ ($q=u,c$) of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.2}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current $tqH$ interactions with a top quark, an up-type quark ($q=u, c$), and a
Standard Model Higgs boson is presented. The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$. 
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.  
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
and $0.072\%$ ($0.036^{+0.017}_{-0.010}\%$), respectively. The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
%}

@@

% Comment deadline
\AtlasCoverCommentsDeadline{1 January 2022}

>>>>

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------
% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current $tqH$ of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.3}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current $tqH$ interactions with a top quark, an up-type quark ($q=u, c$), and a
Standard Model Higgs boson is presented. The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider and corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow qH$. 
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets and event kinematics are used to separate signal from the background through a multivariate discriminant.  
%Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
%No significant excess of events above the background expectation is found,
There is an excess of data events observed above background with a significance of 2.6$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $0.099\%$ ($0.050^{+0.022}_{-0.014}\%$)
and $0.072\%$ ($0.036^{+0.017}_{-0.010}\%$), respectively. The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
%}

@@

% Comment deadline
\AtlasCoverCommentsDeadline{1 March 2022}

### 2022-02-16 sections/data_presel.tex

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-$\tau$ triggers, the $\pt$ threshold of the leading (trailing) $\had$ candidate is 35 (25)~\gev.
Events satisfying the trigger selection are required to have at least one primary vertex candidate.

The signal final state including an electron or muon or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
\begin{itemize}
\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-tagged jet.
\end{itemize}

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & \\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-$\tau$ triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have \pt 1~GeV above the threshold.

The signal final state including an electron or muon or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and subleading $\had$ passed the trigger. Further requirements are defined targeting signal decay modes:
\begin{itemize}
\item $t_h\hadhad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\hadhad$ decay. Exactly two $\had$ with opposite-sign charge are selected, including at least 3 jet with exactly one $b$-tagged jet.
\end{itemize}

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2022-02-16 sections/statistical_analysis.tex

In the absence of signal, exclusion limits are set on $\mu$ , and thus on
$\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

%In the absence of signal,
Exclusion limits are set on $\mu$ , and thus on
$\BR(t\to qH)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
